---
output: github_document
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

```


# Data importing and cleaning

Typically, you will receive a dataset that is most likely in an Excel (`.xlsx` or `.xls`) or `.csv` (comma-separated values) format, which you will have to load and clean before analyzing it. In this template we use the `penguins` sample dataset available in the `palmerpenguins` package, so we don't actually read in any data. Just remember that you can easily do that with the `read_csv` (for csv files), `read_excel`, or `read_dta` (for Stata files) functions. If you want to learn more about reading in data, a tutorial is available on our knowledge-sharing [platform](https://kyso.io/dashboard?s=data&team=ideas42data). 

First, we load all the packages we'll need:

```{r}

library(palmerpenguins)
library(visdat)
library(skimr)
library(tidyverse)
library(tools42)

# Using the penguins dataset
data(penguins)

```

A good way to start is by looking at what variables are available in our dataset, as well as the number of observations. The `skim` function in the `skimr` package is a quick and easy way to summarize this. Consider it a beefed-up replacement of the Stata `summarize` command. You'll see you also get tiny histograms for your continuous data. Visualizing your data is **critical** and you should always, always spend some time plotting it. You won't understand your data unless you plot it.

```{r}

skim(penguins)

```

Great. Looks like most of our data is complete and falls under the expected ranges (that is, there are no crazy values for any of the variables). Let's get a sense of which variables are continuous and which are categorical (character or factor). 

We can do that with the `vis_dat` function, which plots every observation and color-codes it by variable type. We could make it look nicer by adding the i42 theme, since this is a `ggplot` object.

```{r}

vis_dat(penguins_raw) 

```

Isn't this cool? There's also a function to see the degree of missingness for each of our variables. It's called `vis_miss`:

```{r}

vis_miss(penguins_raw) 

```

# Exploratory Analysis

Ok, let's look at the relationships between variables. 

This is interesting. I wonder if there's any differences by species!

```{r}

penguins %>%
  viz_scatter(flipper_length_mm, bill_length_mm) +
  aes(color = species) +
  theme_42() +
  scale_color_manual(values = palette_42("i42_bright"))


```

Now, a histogram of flipper length:


```{r}

penguins %>%
  viz_hist(flipper_length_mm) +
  aes(fill = species) +
  facet_wrap(~species) +
  theme_42() +
  scale_fill_manual(values = palette_42("i42_bright"))


```

# Let's try a regression

```{r preview, fig.height= 7, fig.width=8, dpi=300}

penguins %>%
  ggplot(aes(color = species, x = bill_length_mm, y = flipper_length_mm)) +
  geom_point() +
  theme_42_bright() +
  scale_color_manual(values=palette_42("i42_bright")) +
  labs(title = "This is the penguin plot!",
       subtitle = "A plot of a bunch of penguins belonging to different species")


```


```{r}

model1 <- lm(flipper_length_mm ~ bill_length_mm + species, data = penguins)

summary(model1)

```

And now, a regression table!

```{r}
#library(modelsummary)
library(huxtable)
#options(huxtable.print = print_html)
#options('huxtable.knitr_output_format')
#options(huxtable.knitr_output_format = 'html')


huxreg(model1)

```





